---
output:
  pdf_document: default
  html_document: default
---

```{r , include=FALSE}
#Load libraries 
library(tidyverse)
library(stringr)
library(tidyr)
library(knitr)
library(kableExtra)
library(readxl)
```

# Estate, Inheritances, and Gift Taxes (EIG) {#sec:eig}

## Introduction to the Estate, Inheritances, and Gift Taxes Section

The Estate, Inheritance, and Gift Tax (EIG) section of the GC Wealth Project provides a comprehensive data collection on wealth transfer taxes across countries and over time. The EIG section compiles tax policy information as well as tax revenue data. The section contains information about these taxes for up to over 160 countries, in some instances dating back as far as the 18th century. The EIG section codifies and harmonizes information on features common among these taxes, such as top tax rates among closest relatives, personal tax exemptions, or full tax schedules. The section also provides revenue statistics for EIG taxes from cumulative sources from 1960 onward. Information is obtained from academic, government, and corporate research, government legislation and legislative information, as well as cross-national research and official statistics. 
This chapter introduces the reader to the data structure of the EIG section, as well as the general interpretation and construction of each concept.  


## The `varcode` in the Estate, Inheritance, and Gift Taxes Section

As described in the general warehouse structure section, the `varcode` uniquely identifies each value in the EIG section using five elements. The first element of the `varcode` is a 1-digit code that identifies the `section` of the GC Wealth Project, which for the case of the Estate, Inheritance, and Gift Taxes takes the value `x`. Hence, the `varcode` takes the following form: 

\begin{equation}
\notag \underbrace{\textcolor{blue}{x}}_{\text{Section}} - \underbrace{hs}_{\text{Sector}} - \underbrace{CCC}_{\text{Variable Type}} - \underbrace{DDDDDD}_{\text{Concept}} - \underbrace{ZZ}_{\text{Section Specific}} 
\end{equation}



### `Sector`: Households

The next two letters of the `varcode` indicate the `Sector`, which for this section will always be `hs` for 
households, since these taxes are levied on individuals and estates of private 
citizens. 

### `Variable Type`

The next three letters of the `varcode` represent the `Variable Type`, which will vary in this section. Specifically, five types of variables are used within the EIG section. These are described in Table \ref{tab:eigt_vt}.

```{r eigt_vt, echo=FALSE, comment=NA, message=FALSE, warning=FALSE}

eigt_vt <- read_excel("old/eigt_vartype.xlsx", na = " ") %>%
  mutate_all(~ ifelse(is.na(.), " ", as.character(.)))

eigt_vt %>%
kbl(format="latex", align = "l", booktabs = T, longtable=T, caption = "EIG: Variable Type") %>%
  kable_styling(latex_options = "striped")  %>%
  column_spec(1, width = "1cm") %>%
  column_spec(2, width = "2cm") %>%
  column_spec(3, width = "11cm") 

```



### `Concept`: Variables
The next six letters, indicating `Concept` encode the specific variables for this section, and details for each can be found in Table \ref{tab:EIG_defs}. 

```{r EIG_defs, echo=FALSE, comment=NA, message=FALSE, warning=TRUE}
#\begin{spacing}{1}

#filter EIGT concepts 
source("documentation_warehouse_version.R")
vcdlist <- read_delim(paste0("../../output/databases/dashboards/eigt_warehouse_v", ver, ".csv"), col_select = c('varcode')) %>% unique() %>% separate(varcode, into = c("part1", "part2", "part3", "Code", "part5"), sep = "-") %>%
  select(Code) %>%
  distinct()

# Merge with Dictionary varcode labels
eig_dict <- read_excel("../../handmade_tables/dictionary.xlsx", sheet = "d4_concept") %>%
  select(Code = code, Label = label, Description = description)  %>% 
  inner_join(vcdlist) %>% select(Code, Label, Description)

eig_dict %>%
 kbl(format="latex",align = c('r', 'l', 'l'), 
  caption = "Estate, Inheritance, and Gift Tax Variable Definitions", 
  longtable=TRUE, booktabs = T, linesep = "\\addlinespace")%>% 
  column_spec(1, width="0.8cm")%>% column_spec(2, width="4cm") %>%
  column_spec(3, width="17cm") %>% 
  kable_styling(latex_options = "striped") %>%
  landscape()

```

### `Section Specific`: Bracket Numbers {#subsubsec:brack}

Finally, the last two letters in the `varcode` denote the section-specific variables, which for the EIG section refer to the tax bracket number when needed. Full tax schedule information will vary by tax bracket. For instance, in the event of a flat rate of 10% on individual shares of an inheritance valued at 100,000 currency units, the first bracket (`01`) will cover inheritances worth between 0 and 100,000 currency units and a corresponding tax rate of 0%, while the second bracket (`02`) will cover all inheritances valued over 100,000 with a corresponding tax rate of 10% (see section \ref{subsec:sched}). Information not contained within a tax schedule does not vary by bracket and is contained in the row with bracket number `00`. An example of tax bracket numbers— and the tax schedule more generally—is laid out in Table \ref{tab:eig_ex1}.  



## Data Structure and Interpretation

Downloaded data is provided in long format. All information in the data is sorted by a country's two-letter ISO code (`GEO`), or its full name (`GEO_long`) and `year`. Information unrelated to the tax schedule is listed with `bracket` "00" in the `varcode`, while the schedule variables, which vary within a country-year, have positive bracket values. The final number of observations per country-year varies depending on the number of tax brackets in that country-year (and hence the number of `varcodes`). 

An example illustrated in Table \ref{tab:eig_ex1l} is the UK's tax schedule in 2019. Users can access the tax revenue of `GEO` "UK" by selecting the `value` of the `varcode` corresponding to that `concept` (*x-hs-agg-totrev-00*). Similarly, to display the `value` of the upper bound of the first tax schedule bracket for the UK, the user can select the `varcode` corresponding to that `concept` (*x-hs-thr-ad1ubo-01*). All `varcode` conventions follow the logic detailed in section 5.1.  


```{r eig_ex1l, echo=FALSE, comment=NA, message=FALSE, warning=FALSE}

eig_ex1l <- read_excel("old/eigt_data_ex1_long.xlsx") %>%
  mutate_all(~ ifelse(is.na(.), " ", as.character(.)))


#, linesep = "\\addlinespace"
eig_ex1l %>%
 kbl(format="latex", align = "l",
  caption = "Simplified Illustration of EIG Data in Long Format", 
  booktabs = T)%>% 
  kable_styling(latex_options = "striped") %>% 
  #kable_paper(full_width = F) %>%
   column_spec(1, width="0.53cm")%>% 
   column_spec(2, width="2.95cm")%>% 
   column_spec(3, width="1.55cm")%>% 
   column_spec(4, width="1.5cm") %>% 
   column_spec(5, width="8cm") 
  # column_spec(6, width="0.8cm")%>%
  # column_spec(7, width="1.4cm")%>%
  # column_spec(8, width="0.7cm")
  #column_spec(8, width="0.5cm")

```

```{r eig_ex1, echo=FALSE, comment=NA, message=FALSE, warning=FALSE}

eig_ex1 <- read_excel("old/eigt_data_ex1.xlsx", na = " ") %>%
  mutate_all(~ ifelse(is.na(.), " ", as.character(.)))

eig_ex1 %>%
 kbl(format="latex",
  caption = "Simplified Illustration of a Tax Schedule", 
  booktabs = T, linesep = "\\addlinespace")%>% 
  kable_styling(latex_options = "striped")

```

If transformed into wide format, any observation is uniquely identified by country, year, and tax bracket to accommodate full tax schedules. That is, variables containing tax schedule information vary within each country-year. Hence, information will look considerably different from the example detailed in Table \ref{tab:eig_ex1l} above. 

To illustrate a wide structure, consider the UK tax schedule in 2019. There is a flat tax of 40 percent on estates over GBP 325,000. The revenue for the UK under the estate tax in 2019 was GBP 5.165 billion. A simplified subset of the variables (non-identifying variable names changed for ease of explanation) is shown in Table \ref{tab:eig_ex1}. As this example illustrates, selecting `GEO` "UK" and `year` "2019" will not be sufficient to uniquely identify one observation per country. For instance, any user interested in total revenue information would need to additionally select `bracket` "0". Importantly, variables that are not related to the tax schedule will not be filled for country-year observations other than in the zero bracket.





### Non-Schedule Tax Parameters

#### Binary Indicators for Tax Status

A set of binary variables is used to indicate whether a country 
or region has any wealth transfer taxes (*eigsta*), as well as 
the specific types of taxes that are levied (*esttax*, *inhtax*, 
*giftax*), when applicable. Taxes that are not deemed estate- 
or inheritance-specific taxes may be indicated as either “$Y$\” 
(yes) or “$N$\” (no) for the binary 
variables, but have their schedules, rates or exemption information 
filled. There may therefore be inconsistencies between these 
variables; for instance, Colombia does not tax inheritances or 
estates specifically, but includes them as capital gains—data 
for Colombia indicates that an inheritance tax and a gift tax 
are present; however, the revenue information shows no government 
revenues for these taxes. Countries for which no data is 
available other than the tax revenue from the OECD are marked 
as having an estate, inheritance, or gift tax if the revenue 
information is non-zero and not decreasing as a pattern, which 
would indicate a possible repeal. When possible, the data further include 
a variable indicating the first year for which any wealth 
transfer tax has been levied in a country or region (*eigfir*) [@GenschelSeelkopf2019].


#### Tax Reductions and Relationship-Based Parameters {#subsubs:reb}

Estate and inheritance tax exemptions can vary in complexity and detail, 
and countries differ in how they offer reductions to the final 
tax bill (exemptions, deductions, rebates, credits, *etc.*). The data 
in this section encode these as "exemptions", for instance, by 
calculating how much of an estate or inheritance would be exempt under a credit. 


Inheritance taxes frequently vary in generosity of exemptions or rates 
by the closeness of relationship between decedents and recipients, 
which are divided into "classes." If this is the case, *itaxre* will be 
"Y." The data pick up the exemptions (*chiexe*) and rates 
for direct descendants without any additional mitigating factors (for 
instance, higher exemptions or lower rates for minors). Because 
classes of inheritors are not generally applicable for estate taxes, 
information in country-years with estate taxes tends to 
apply to everybody, and the exemptions and rates apply to the 
aggregate of all property bequeathed by a decedent. The exception to 
this is if a country with estate taxes has an estate tax, but individual 
share-based exemptions vary beyond those for spouses and minor 
children. In this case, the indicator *ieexem* will contain the value "$Y$,\" and the 
corresponding exemptions indicate the exemption applicable to the 
proportion of the estate that corresponds to direct descendant's shares, 
even though the tax is paid on the overall estate. 


In cases where *eigsta* indicates the existence of an EIG tax, a missing value for *chiexe* means that inheritances (or the respective portions of estates) are fully exempt for direct descendants if *toprat* is equal to zero. 
When tax rates cannot be determined without determining additional 
information about the recipient or decedent, assumptions are made in 
order to select the lowest applicable rates for direct descendants. In 
Spain, for instance, the tax rates vary by relationship and increase 
with the pre-existing wealth owned by the recipient. The data is 
entered under the assumption that the recipient possesses no 
pre-existing wealth. For such cases, however, more information will 
be made available in the metadata.


### Tax Schedules {#subsec:sched}

#### General Structure and Interpretation


Progressive tax schedules are split into brackets by the value of the estate or inheritance, each with identical variable values for non-schedule variables. Bracket number, the dashboard-specific variable 
encoded in the last two letters of the `varcode`, specifies the order of
the brackets that constitute a full tax schedule. 

The structure of the tax schedule data is the same as the statutory schedules
provided by many governments for estate taxes and other progressive taxes.
The basic structure of all tax schedules in the data consists of tax 
brackets arranged in ascending order, which indicate the range of amounts 
to which a tax rate applies, as well as the tax liability on amounts 
below that bracket. Each bracket corresponds to a single row, and all brackets
that form a schedule have the same logistical variable values; all non-schedule 
tax variables are constant for a schedule, and therefore identical for all 
brackets (or rows).

The schedules are typically cumulative in structure, such that the rate in a bracket that corresponds to an aggregate inherited (or estate) value only 
applies to the proportion of the inheritance that is greater than the highest 
amount in the previous bracket. That is, if the inherited amount misses a 
lower tax bracket by one currency unit, the higher tax rate only applies 
to one currency unit.



#### Schedule Transformation for Adjusted Schedules

We adjust the schedules to make them more comparable across countries, as detailed below. 

Estate, inheritance, and gift taxes typically only apply above a certain threshold. 
We modify all schedules that do not already include a bracket with a zero tax rate that 
corresponds to the exempted amount (that is, a zero tax rate on amounts
ranging from zero to the exemption threshold), to include such a bracket.
This can be complicated because tax schedules are not standardized with respect
to exemptions. Some exemptions might be included in a tax schedule and do not 
require any additional calculation. Others are calculated as deductions or 
credits, which means that a tax is calculated on the entirety of the estate, 
and the tax that would be owed on the exemption amount is subsequently 
subtracted from the total tax liability. For instance, consider the U.S. federal estate tax: The statutory schedule contains a progressive 
schedule, but because the exemption deduction is so high (nearly 13 million 
USD as of 2023), every bracket but 
the last is effectively 
within the deduction range. Therefore (assuming no other deductions or credits
apply), all amounts below (and many above) the 
last bracket would yield a final tax bill of zero. The result is a flat tax 
rate that applies to relatively large estates of several million dollars. 

In order to transform tax schedules to adjusted and effective, 
we assume that taxes will be paid on a monetary
transfer to one adult child upon the death of a decedent, assuming no
additional circumstantial deductions, reliefs, or credits apply unless
otherwise specified. In the case of a country like Spain, it is additionally assumed that the recipient owns no prior wealth. Historical information is adjusted to reflect the most recent local currency.



#### Regional Information

As of the public release v.2, the data also include regional-level tax information for all U.S. states. Varcodes and variables for the regional level adhere to the database structure outlined above. We note some important conceptual differences:

First, the tax status variables (*eigsta*, *esttax*, *inhtax*, *giftax*) refer to the existence of a tax at the state-level, irrespective of federal taxes that also apply within state boundaries. Thus, if a given state indicates *esttax* = "N", estates in that state can still be subject to the federal estate tax, if it applies. 

Second, adjusted tax schedule variables (e.g., *chiexe*, *ad1lb*, *ad1ub*, etc.) combine full tax schedule information of federal- and state-level taxes. That is, EIG taxes levied by the state can provide adjustments of the statutory schedule depending on interactions with the federal tax. Thus, our state-level adjusted schedules take the joint structure of taxes at both levels into account in order to arrive at tax exemptions, brackets, and marginal rates that are readily comparable across states within the U.S.

Third, top marginal tax rate variables (e.g., *toprat*) also indicate the combined information of the federal estate tax and state estate, inheritance, and gift taxes. Combining the federal estate tax and gift and inheritance taxes at the state level yields harmonized top marginal tax rates across states, however, we cannot provide separate top rates by type of tax as combining taxes at different levels jointly yields the adjusted top rates. All top rates and adjusted schedules thus refer to adult, direct descendants without siblings.

Fourth, state and federal tax interactions can lead to marginal tax structures with spikes within the tax bracket structure. Put differently, the highest tax rate in an adjusted schedule might be in a lower bracket and inheritances above that bracket will be subject to lower rates. In such cases, the top marginal tax rate refers to the last bracket in the (progressive) tax schedule rather than to the highest tax rate.




